### 2014-03-13 Draft/evaluation.tex
Added parts of evaluation

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
	identifying temporal constraints from sentences written in natural language?
	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from specification sentences in the API documents? 
\end{itemize}

@@

\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline API & Methods & No. of Sentences & Spec Sentences & ICON Ann & TP & FP & FN & P & R & F-Score \\ 
\hline java.io &  & 2417 & 78 & 87 & 56 & 31 & 22 & 64.4 & 71.8 & 67.9 \\ 
\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 \\ 
\hline Total &  & 3909 & 90 & 99 & 64 & 35 & 26 & 64.6$^*$ & 71.1$^*$ & 67.7$^*$ \\ 
\hline
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{6.5in}}{\footnotesize $^*$ Column average; TP: Total number of True Positives; 
FP: Total number of False Positives; FN: Total number of False Negatives; P: Precision; R: Recall} \\ 
\end{tabular}
\end{center}
\end{table*}

@@

In this section, we quantify the effectiveness of \tool\ in identifying specification sentences by answering RQ1. Our results show that, out of 2,414 sentences, \tool\ effectively identifies specification sentences with the average precision, recall, F-score, and accuracy of 65.0\%, 71.8\%, 68.7\%, and 97.9\%, respectively.

We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence. \textbf{A example goes here}

We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence (producing false positives). For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. \tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''. However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method. \tool, thus incorrectly identifies the sentence as a specification sentence.

@@

We next present an example to illustrate how \tool\ fails identify a specification sentence (producing false negative). False negatives are particularly undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API document. Furthermore, an overwhelming number of false negatives works against the usefulness of \tool. For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. The sentence describes the constraint in terms of invoking the same method again. Although \tool\ correctly identifies the method \CodeIn{close} in the sentence, \tool\ currently does not support temporal constraint on the same method. Aforementioned, limitation causes \tool\ to not identify the statement as a specification constraint.

@@

>>>>

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
	identifying temporal constraints from sentences written in natural language?
	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from specification sentences in the API documents?
	\item\textbf{RQ3}: How do the constraints inferred by our approach compare with the typed-enforced temporal constraints?

\end{itemize}

@@

\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline API & Methods & Sentences & Spec Sentences & \tool\ Ann & TP & FP & FN & P(\%) & R(\%) & F-Score(\%) \\
\hline 
\hline java.io &  & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 \\ 
\hline AMAZON S3 REST & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 \\ 
\hline Total &  & 3909 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ \\ 
\hline
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{6.5in}}{\footnotesize $^*$ Column average; TP: Total number of True Positives; 
FP: Total number of False Positives; FN: Total number of False Negatives; P: Precision; R: Recall} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

@@

In this section, we quantify the effectiveness of \tool\ in identifying specification sentences by answering RQ1.
Table~\ref{tab:results} shows the effectiveness of \tool\ in identifying specification sentences.
Column ``API'' lists the names of the subject API. 
Column ``Methods'' and ``Sentences'' lists the number of methods and sentences in each subject API's.
Column ``\tool\ Ann'' lists the number of sentences identified by \tool\ as constraint sentences. 
Columns ``TP'', ``FP'', ``TN'', and ``FN'' represent the number of \CodeIn{true positives}, \CodeIn{false positives}, \CodeIn{true negatives}, and \CodeIn{false negatives}, respectively. 
Columns ``P(\%)'', ``R(\%)'', and ``F-Score(\%)'' list percentage values of \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} respectively. 
Our results show that, out of 3,909 sentences, \tool\ effectively identifies specification sentences with the average precision, recall, and F-score of 65.0\%, 72.2\%, and 68.4\%, respectively.

%We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence. \textbf{A example goes here}
We next present an example to illustrate how \tool\ incorrectly identifies a sentence as a specification sentence (producing false positives). For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. \tool\ incorrectly identifies the action ``flush'' being performed before the action ``close''. However \tool\ fails to make the distinction that it happens internally (enforced within the body) in the method. \tool, thus incorrectly identifies the sentence as a specification sentence.

@@

We next present an example to illustrate how \tool\ fails identify a specification sentence (producing false negative). False negatives are undesirable in the context of our problem domain, because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents. Furthermore, an overwhelming number of false negatives works against the usefulness of \tool. For instance, consider the sentence ``\textit{This is done by flushing the stream and then closing the underlying output stream.}'' from  \CodeIn{close} method description from \CodeIn{PrintStream} class. The sentence describes the constraint in terms of invoking the same method again. Although \tool\ correctly identifies the method \CodeIn{close} in the sentence, \tool\ currently does not support temporal constraint on the same method. Aforementioned, limitation causes \tool\ to not identify the statement as a specification constraint.

@@

\subsubsection{RQ3: Comparison to Typed-Enforced Constraints}

In this section, we compared the temporal constraints inferred from the natural language API descriptions to those enforced by the type-system. For answering this question we used the constraints inferred by the Algorithm~\ref{alg:TypeAnalysis} presented in Section~\ref{sec:approach} on classes in \CodeIn{java.io} package.

We observed that the constraints inferred by our \tool\ from natural language text were distinct from the constraints enforced by the type system.
